\chapter{User Stories}
\section{Actors}
\begin{itemize}
\item{\textbf{Government}: Use given information to set up invoices.}
\item{\textbf{User}: Use the internet to keep track of their invoices.}
\item{\textbf{Police}: Can trace stolen car's location.}
\item{\textbf{Developer}: Test the system without touching real data}
\end{itemize}

\section{Epics}
\begin{itemize}
 \item Create a simulation for developers to virtually test the system in a safe environment.
 \item Store, retrieve, monitor and filter the movements of vehicles across the country.
\end{itemize}

\section{Stories}
\subsection{First Epic}
\begin{enumerate}
	\item As a developer I want to generate uniquely identifiable vehicles for multi-vehicle testing.
	\item As a developer I want to generate test zones for testing different rates.
	\item As a developer I want to move generated vehicles over actual roads as a proof of concept for realism.
	\item As a developer I want to accurately control the time steps of the simulation so that I have full control over my testsimulation.
	\item As a developer I want to use a selected number of vehicles for simulation so that I can run tests with mock data on a smaller scale.
	\item As a developer I want to only generate test data for a certain area so that I can run tests with mock data on a smaller scale.
	\item As a developer I want to store the simulations in a separate, filterable store.
\end{enumerate}]

\subsection{Second Epic}
\begin{enumerate}
	\item As a user I want to be able to read the platform in multiple languages because I might not necessarily speak the language used in my country.
	\item As a user I want to safely register an account so I have my personal account containing all information relevant to me.
	\item As a user I want to keep track of my invoices so that I know how much money I have paid or will have to pay.
	\item As a user I want to keep track of my vehicles so that I can own multiple vehicles, their locations and invoices.
	\item As a user I want to have an insight into the vehicle movements of the vehicles I own.
	\item As a user I want to safely pay my invoices online so that I can safely, directly, pay for any invoices from home
	\item As a user I want to see and edit my personal data so that I can easily check and update my information.
	\item As a user I want to report my car as stolen so that the police is aware they’ll have to look for my vehicle.
	\item As a user I want to view the ownership history and the stolen reports.
	\item As the police I want to confirm or report a vehicle as stolen so that the system is aware that I want a notification when the stolen car has been spotted..
	\item As the police I want to see the location history of a vehicle reported as stolen so that I’ll be able to find where the vehicle has been in the past.
	\item As the police I want to see the ownership history of a stolen vehicle.
	\item As the police I want to follow a stolen vehicle in real time so that I can find it in case I lose it during a specific event such as a car chase.
	\item As the police I want to record when an unknown foreign vehicle enters so that I can invoice them for driving on this country’s roads.
	\item As the police I want to have a live overview of foreign vehicles so that I know who and when enters my country.
	\item As the police I want to mark a vehicle as unstolen so that everyone knows a stolen car has been retrieved.
	\item As the government I want to mark an area with a specific rate so that specific areas can differing rates.
	\item As the government I want to see if a vehicle is registered to an active site user so that I can see whether they’re using the application.
	\item As the government I want to store a movement history of every vehicle so that I can see a vehicle’s past movement.
	\item As the government I want to invoice the users so that they know when and how much money they own me..
	\item As the government I want to see the hardware used to report a location so that I can filter on suppliers.
	\item As the government I want to add and modify vehicles with trackers so that newly bought vehicles can be added to the system.
	\item As the government I want to add specific rates for kilometres driven so that different rates could apply depending on the driven kilometres.
	\item As the government I want to automatically recalculate an invoice so that user complaints and/or technical issues can be easily handled and possibly resolved.
	\item As the government I want to see automatically generated invoices so that I can see whether an invoice has been produced correctly.
	\item As the government I want a clear view into the system status so that I can overview all overviews when it comes to amount of sent invoices, users and updates.
	\item As the government I want to filter the invoices so that I can find invoices based on specific attributes.
	\item As the government I want to mark invoices as paid or cancelled so that I have a clear list of invoice statuses.
	\item As a developer I want the website to update with new data every ten minutes so that the user always has the most recent information.
	\item As a developer I want to mark users with groups so that certain users will be able to use this group’s privileges.
	\item As a developer I want to grant specific privileges to groups so that said groups can perform specific tasks.
	\item As a government I want to share details on cars and users with other countries that we have an agreement with.
	\item As a government I want  to request data of foreign vehicles from countries we have an agreement with.
	\item As the police we want to report when a stolen foreign vehicle entering the country so that illegal car trade is less likely to happen.
	\item As the police we want to receive a report when a stolen vehicles goes abroad so that illegal car trade is less likely to happen.
	\item As a developer I want to trigger an alarm when a vehicle moves in an impossible way so that possible fraud can be prohibited.
	\item As a developer I want to monitor system status so that I always have a clear insight on how the system is running..
	\item As a developer I want to scale the system so that I can avoid technical problems without giving users any trouble.